Multi-period and Multi-product Batch Processing Time Maximization Problem

### 2023-07-31 multi-period/manuscript.tex
updating paper
math model

$\textrm{UI}_{i0}$ is the initial free factory storage of product $i$ on the beginning of the (\emph{first}) planning day;

$\textrm{UI}_{i0}$ is the maximum quantity allowed for stocking in the factory the product $i$ on the (\emph{first}) planning day; \\

$\textrm{I}_{d}$ is the maximum quantity allowed for additional factory storage of all products on day $d$;

$\textrm{UI}_{id}$ is the maximum quantity allowed for stocking in the factory the product $i$ on day $d$;

@@

@@

$I_{id}$ is the amount of product $i$ that will be stored at the factory on day $d$;

>>>>

@@

$UI_{id}$ is the maximum quantity allowed for stocking in the factory the product $i$ on day $d$;

being $\textrm{UI}_{i0}$ the maximum quantity allowed for stocking in the factory the product $i$ on the (\emph{first}) planning day ($d=1$);

$I_{d}$ is the free factory storage of all products on the end of the day $d$;

being $\textrm{I}_{0}$ the initial free inventory for all products on factory on the start of the (\emph{first}) planning day ($d=1$); \\

@@
